Article data analysis

### 2018-10-12 notebooks/article_notebook.Rmd
updated with figures on read number densities

```{r, include=FALSE}
id <- c("2017-01-3941-1-S", "2016-17-98-1-S", "2016-17-610-1-S", "2016-17-604-1-S", 
"2016-17-565-1-S", "2016-17-550-1-S", "2016-17-548-1-S", "2016-17-546-1-S", 
"2016-17-485-1-S", "2016-17-469-1-S", "2016-17-423-1-S", "2016-17-412-1-S", 
"2016-17-408-1-T", "2016-17-408-1-S", "2016-17-393-1-S", "2016-17-391-1-S", 
"2016-17-388-1-T", "2016-17-388-1-S", "2016-17-377-1-S", "2016-17-363-1-S", 
"2016-17-352-1-S", "2016-17-343-1-S", "2016-17-340-1-S", "2016-17-336-1-S", 
"2016-17-329-1-S", "2016-17-299-1-S", "2016-17-298-1-S", "2016-17-294-1-S", 
"2016-17-292-1-S", "2016-17-288-1-S", "2016-17-281-1-T", "2016-17-281-1-S", 
"2016-17-275-1-S", "2016-17-271-1-S", "2016-17-27-1-S", "2016-17-264-1-S", 
"2016-17-263-1-S", "2016-17-257-1-S", "2016-17-256-1-S", "2016-17-242-1-S", 
"2016-17-225-1-S", "2016-17-224-1-S", "2016-17-189-1-T", "2016-17-183-1-S", 
"2016-17-174-1-T", "2016-17-174-1-S", "2016-17-164-1-S", "2016-17-16-1-S", 
"2016-17-148-1-S", "2016-17-124-1-S", "2016-17-114-1-S", "2016-17-105-1-T", 
"2016-17-1-1-S", "2016-02-785-2-S", "2016-02-783-2-T", "2016-02-771-2-S", 
"2016-02-770-2-S", "2016-02-741-2-S", "2016-02-739-2-S", "2016-02-732-2-S", 
"2016-02-727-2-S", "2016-02-726-2-S", "2016-02-725-2-S", "2016-02-723-2-S", 
"2016-02-697-2-S", "2016-02-693-2-T", "2016-02-693-2-S", "2016-02-692-2-S", 
"2016-02-690-2-T", "2016-02-690-2-S", "2016-02-620-2-S", "2016-02-563-2-S", 
"2016-02-546-2-S", "2016-02-543-2-S", "2016-02-531-2-S", "2016-02-522-2-S", 
"2016-02-515-2-T", "2016-02-515-2-S", "2016-02-514-2-S", "2016-02-513-2-T", 
"2016-02-513-2-S", "2016-02-505-2-S", "2016-02-492-2-S", "2016-02-490-2-S", 
"2016-02-486-2-S", "2016-02-447-2-S", "2016-02-446-2-S", "2016-02-428-2-S", 
"2016-02-425-2-S", "2016-02-419-2-S", "2016-02-418-2-S", "2016-02-415-2-S", 
"2016-02-413-2-T", "2016-02-413-2-S", "2016-02-411-2-S", "2016-02-410-2-S", 
"2016-02-409-2-S", "2016-02-408-2-S", "2016-02-402-2-S", "2016-02-381-2-S", 
"2016-02-369-2-S", "2016-02-366-2-S", "2016-02-363-2-S", "2016-02-359-2-S", 
"2016-02-358-2-S", "2016-02-356-2-S", "2016-02-353-2-S", "2016-02-352-2-S", 
"2016-02-351-2-S", "2016-02-348-2-S", "2016-02-345-2-T", "2016-02-345-2-S", 
"2016-02-343-2-S", "2016-02-336-2-S", "2016-02-330-2-S", "2016-02-329-2-S", 
"2016-02-324-2-S", "2016-02-316-2-S", "2016-02-302-2-S", "2016-02-293-2-S", 
"2016-02-281-2-S", "2016-02-278-2-S", "2016-01-3763-1-T", "2016-01-3474-1-T", 
"2015-01-753-1-S", "2015-01-752-1-S", "2015-01-751-1-S", "2015-01-750-1-S", 
"2015-01-749-1-S", "2015-01-5263-1-S", "2015-01-5262-1-S", "2015-01-5177-1-S", 
"2015-01-5141-1-S", "2015-01-5140-1-S", "2015-01-5138-1-S", "2015-01-5022-1-S", 
"2015-01-5020-1-S", "2015-01-5018-1-S", "2015-01-4988-1-S", "2015-01-4934-1-S", 
"2015-01-4932-1-S", "2015-01-4931-1-S", "2015-01-4794-1-S", "2015-01-4788-1-S", 
"2015-01-4742-1-S", "2015-01-467-1-S", "2015-01-466-1-S", "2015-01-463-1-S", 
"2015-01-4559-1-S", "2015-01-4558-1-S", "2015-01-4465-1-S", "2015-01-4463-1-S", 
"2015-01-4462-1-S", "2015-01-4421-1-S", "2015-01-4249-1-S", "2015-01-4037-1-S", 
"2015-01-3915-1-S", "2015-01-3914-1-S", "2015-01-3911-1-S", "2015-01-3887-1-S", 
"2015-01-3640-1-S", "2015-01-3639-1-S", "2015-01-3638-1-S", "2015-01-3548-1-S", 
"2015-01-3545-1-S", "2015-01-3318-1-S", "2015-01-3317-1-S", "2015-01-3102-1-S", 
"2015-01-3004-1-S", "2015-01-3001-1-S", "2015-01-2879-1-S", "2015-01-2878-1-S", 
"2015-01-2839-1-S", "2015-01-2838-1-S", "2015-01-2837-1-S", "2015-01-2836-1-S", 
"2015-01-2835-1-S", "2015-01-2771-1-S", "2015-01-2430-1-S", "2015-01-2429-1-S", 
"2015-01-2426-1-S", "2015-01-2404-1-S", "2015-01-2403-1-S", "2015-01-2309-1-S", 
"2015-01-2166-1-S", "2015-01-2097-1-S", "2015-01-2094-1-S", "2015-01-1955-1-S", 
"2015-01-1954-1-S", "2015-01-1952-1-T", "2015-01-1951-1-S", "2015-01-1950-1-S", 
"2015-01-1949-1-S", "2015-01-1826-1-S", "2015-01-1823-1-S", "2015-01-1661-1-S", 
"2015-01-1566-1-S", "2015-01-1343-1-S", "2014-01-861-1-S", "2014-01-860-1-S", 
"2014-01-856-1-S", "2014-01-7584-1-S", "2014-01-7543-1-S", "2014-01-7512-1-S", 
"2014-01-7490-1-S", "2014-01-7479-1-S", "2014-01-7443-1-S", "2014-01-7442-1-S", 
"2014-01-7394-1-S", "2014-01-7375-1-S", "2014-01-7234-1-S", "2014-01-7207-1-S", 
"2014-01-7136-1-S", "2014-01-7133-1-S", "2014-01-7050-1-S", "2014-01-6926-1-S", 
"2014-01-6924-1-S", "2014-01-6710-1-S", "2014-01-6625-1-S", "2014-01-6530-1-S", 
"2014-01-6291-1-S", "2014-01-6123-1-S", "2014-01-6122-1-S", "2014-01-6044-1-S", 
"2014-01-6043-1-S", "2014-01-6041-1-S", "2014-01-6040-1-S", "2014-01-5917-1-T", 
"2014-01-5917-1-S", "2014-01-5916-1-S", "2014-01-5915-1-S", "2014-01-5912-1-S", 
"2014-01-5792-1-S", "2014-01-5565-1-S", "2014-01-4922-1-T", "2014-01-4921-1-S", 
"2014-01-4651-1-S", "2014-01-4539-1-S", "2014-01-4271-1-S", "2014-01-4270-1-S", 
"2014-01-3802-1-S", "2014-01-3677-1-S", "2014-01-3676-1-S", "2014-01-3212-1-S", 
"2014-01-2996-1-S", "2014-01-2995-1-S", "2014-01-2992-1-S", "2014-01-2773-1-S", 
"2014-01-2728-1-S", "2014-01-2516-1-S", "2014-01-2366-1-S", "2014-01-2362-1-T", 
"2014-01-2145-1-S", "2014-01-2144-1-S", "2014-01-2071-1-S", "2014-01-2070-1-S", 
"2014-01-2069-1-S", "2014-01-1742-1-S", "2014-01-1741-1-S", "2014-01-1649-1-S", 
"2014-01-1268-1-T", "2014-01-1182-1-S", "2013-01-2024-1-T", "2012-01-838-6-T", 
"2011-01-9386-3-T", "2011-01-6927-5-T", "2011-01-3460-5-T", "2011-01-1544-2-T", 
"2010-01-991-7-T", "2009-01-551-1-T", "2009-01-4672-5-T", "2009-01-4618-2-T", 
"2009-01-4415-4-T", "2009-01-413-1-T", "2009-01-4064-1-T", "2009-01-3815-1-T", 
"2009-01-3064-2-T", "2009-01-2696-4-T", "2009-01-2521-3-T", "2009-01-175-4-T", 
"2009-01-175-2-T", "2009-01-1690-1-T", "2007-01-361-1-T", "2006-01-2821-1-T", 
"2006-01-2184-1-T")

```{r Import data, include = FALSE}
isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

no_of_reads <- read.table("../data/read_data.txt",
                          sep = "\t",
                          header = T,
                          stringsAsFactors = F)

```{r ARIBA analysis, include = FALSE}
megares_report_loc <- "../data/ariba/megares_results"
resfinder_report_loc <- "../data/ariba/resfinder_results"
ac_genes <- c("qnr","aac","oqx")
mut_genes <- c("gyr","par","marR","soxS","tolC","acrR")

@@

# -------------------------------------- Functions
# Collapses data frame to unique lines while ignoring NA's
func_paste <- function(x) paste(unique(x[!is.na(x)]), collapse = ", ")

@@

# Function that returns info on flag selection
check_flags <- function(df) {
  df <- df %>%
    select(ref, gene_names, flag, ref_ctg_change) %>%
    mutate(flag_result = flag %in% flag_selection,
           flag_result = as.integer(flag_result),
           ref = gsub("(.*?)\\_.+", "\\1", ref),
           ref = sub("^\\d*-?(\\d{4}-.*)", "\\1", ref),
           ref = sub("^(\\d{4}-\\d{2}-\\d*)-1", "\\1", ref)) %>%
    rename("gene" = gene_names)
  return(df)
}

# Function that handles megares data and returns a data frame with information on whether a gene
# is mutated or not. Includes control for QRDR in gyrA.
create_mut_table <- function(df) {
  df <- df %>%
    select(ref, gene_names, flag, ref_ctg_change) %>%
    filter(flag %in% flag_selection) %>%
    mutate(id = 1:n()) %>%
    spread(gene_names, ref_ctg_change) %>%
    group_by(ref) %>%
    summarise_all(funs(func_paste)) %>%
    select(-c(id, flag)) %>%
    gather(gene, mut, -ref) %>%
    mutate(mut = ifelse(mut == "" | mut == "." | is.na(mut) == TRUE, 0, mut),
           result = ifelse(mut != 0, 1, 0),
           result = as.integer(result),
           type = "mut")
  return(df)
}

@@

# creates a data frame with one row per sample, and 1/0 results 
# for mutations in respective genes in columns
create_mut_report <- function(df) {
  df <- df %>%
    select(-mut) %>%
    group_by(ref) %>%
    mutate(id = 1:n()) %>%
    spread(gene, result_total) %>%
    summarise_all(funs(func_paste)) %>%
    select(-c(id, type))
  return(df)
}

# creates a data frame with one row per sample, and 1/0 results
# for acquired genes in columns
create_acquired_report <- function(df) {
  df <- df %>%
    group_by(ref) %>%
    mutate(id = 1:n()) %>%
    spread(gene, result_total) %>%
    summarise_all(funs(func_paste)) %>%
    select(-c(id, type))
  return(df)
}

# prepares data frame for number of mutations heatmap
create_heatmap_df <- function(df) {
  qnr <- names(df)

  qnr_cols <- c()

  for (i in qnr) {
    if (grepl("qnr", i, ignore.case = TRUE) == TRUE) {
      qnr_cols <- c(qnr_cols, i)
    }
  }

  qnr_df <- df %>%
    select_at(vars(ref, qnr_cols)) %>%
    gather(gene, result, -ref) %>%
    mutate(type = "Gene")

  qnr_mut_quant <- mut_quant %>%
    select(-c("gyrA","gyrB","parC","parE")) %>%
    mutate(type = "Mut") %>%
    gather(gene, result, -c(ref, type)) %>%
    mutate(gene = case_when(gene == "mut_gyrA" ~ "gyrA",
                            gene == "mut_gyrB" ~ "gyrB",
                            gene == "mut_parC" ~ "parC",
                            gene == "mut_parE" ~ "parE",
                            TRUE ~ gene)) %>%
    rbind(., qnr_df)
  return(qnr_mut_quant)
}

@@

# Check flags
mut_flags <- check_flags(clean_mut_data)
acquired_flags <- check_flags(clean_acquired_data)

# Wrangle
mut_table <- create_mut_table(clean_mut_data)
mut_table_fixed <- fix_gyr_par_results(mut_table)
mut_filtered <- filter_mut_table(mut_table_fixed)
acquired_table <- create_acquired_table(clean_acquired_data)
acquired_filtered <- filter_acquired_table(acquired_table)

@@

mut_quant <- suppressWarnings(calc_no_of_mut(mut_table))
heatmap_df <- create_heatmap_df(acquired_report)

@@

# Figures
## Percent QREC isolates with mutations in intrinsic genes
```{r}
gene_names <- names(mut_report)

gene_names <- gene_names[-1]

mut_report %>%
    mutate(
      ref = gsub("(.*?)\\_.+", "\\1", ref),
      ref = sub("^\\d*-?(\\d{4}-.*)", "\\1", ref),
      ref = sub("^(\\d{4}-\\d{2}-\\d*)-1", "\\1", ref)
    ) %>%
    arrange(desc(ref)) %>%
    mutate(id = id) %>%
    left_join(isolate_data, by = "id") %>%
    gather(key, value, gene_names) %>%
    group_by(key, value, species) %>%
    count() %>%
    ungroup() %>%
    mutate(value = if_else(value == 1, "Present", "Absent")) %>%
    spread(value, n, fill = 0) %>%
    rowwise() %>%
    mutate(
      Total = Present + Absent,
      Percent = round(Present / Total * 100, 1),
      lwr = round(get_binCI(Present, Total)[1], 1),
      upr = round(get_binCI(Present, Total)[2], 1)
    ) %>%
    ggplot(aes(key, Percent, fill = species)) +
    geom_col(color = "black",
             position = position_dodge(1)) +
    geom_errorbar(
      aes(ymin = lwr, ymax = upr),
      width = 0.6,
      position = position_dodge(1)
    ) +
    scale_x_discrete(limits = c(
      "gyrA", "gyrB", "parC", "parE",
      "marR", "soxS", "tolC"
    )) +
    scale_fill_brewer(palette = "Paired") +
    labs(y = "Percent (%) of isolates") +
    guides(fill = FALSE) +
    theme_classic() +
    theme(
      axis.text.x = element_text(
        angle = 90,
        size = 12,
        hjust = 1,
        vjust = 0.4
      ),
      axis.title.x = element_blank(),
      axis.text.y = element_text(size = 12),
      axis.title.y = element_text(size = 14),
      strip.text = element_text(size = 12)
    ) +
    facet_wrap(~ species)
```

>>>>

```{r Import data, include = FALSE}

# Collapses data frame to unique lines while ignoring NA's
func_paste <- function(x) paste(unique(x[!is.na(x)]), collapse = ", ")

id_data <- read.table("../data/id.txt",
                      sep = "\t",
                      header = TRUE,
                      stringsAsFactors = F)

isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

two_reads <- read.table("../data/no_of_reads.txt",
                          sep = "\t",
                          header = F,
                          stringsAsFactors = F) %>%
  rename("ref" = V1,
         "reads" = V2) %>%
  mutate(ref = gsub(".+/(.*?)\\.fastq\\.gz", "\\1", ref),
         type = ifelse(grepl("R1", ref) == TRUE, "R1", "R2")) %>%
  mutate(ref = gsub("(.*?)_L00[0-9]_R[1-2]_00[0-9]","\\1", ref)) %>%
  group_by(ref) %>%
  mutate(id = n()) %>%
  {. ->> four_reads} %>%
  filter(id == 2) %>%
  spread(type, reads) %>%
  rename("R1-1" = R1,
         "R2-1" = R2) %>%
  mutate("R1-2" = NA,
         "R2-2" = NA) %>%
  select(-id) %>%
  mutate_all(funs(as.character(.)))

four_reads <- four_reads %>%
  filter(id == 4) %>%
  group_by(ref) %>%
  mutate(id = 1:n()) %>%
  spread(id, reads) %>%
  summarise_all(funs(func_paste)) %>%
  rename("R1-1" = `1`,
         "R2-1" = `2`,
         "R1-2" = `3`,
         "R2-2" = `4`) %>%
  select(-type) %>%
  mutate_all(funs(as.character(.)))

no_of_reads <- as.data.frame(rbind(as.matrix(two_reads), as.matrix(four_reads))) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref)

mic_data <- read.table("../data/mic_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

mlst_hf150bp <- read.table("../data/mlst/hiseq_flex_150bp_mlst_summarized_results.tsv",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

mlst_hx125bp <- read.table("../data/mlst/hiseq_xt_125bp_mlst_summarized_results.tsv",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

mlst_hrx250bp <- read.table("../data/mlst/hiseqr_xt_250bp_mlst_summarized_results.tsv",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

mlst_data <- rbind(mlst_hf150bp, mlst_hx125bp, mlst_hrx250bp) %>%
  separate(ST.adk.fumC.gyrB.icd.mdh.purA.recA,
           into = c("x","ST","adk","fumC","gyrB","icd","mdh","purA","recA"),
           sep = " ") %>%
  select(-x) %>%
  rename("ref" = header) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref)
```

# Sequence data
## Distribution of number of reads per sequencer
```{r}
sequence_data <- no_of_reads %>%
  left_join(isolate_data, by = "id") %>%
  mutate_at(vars(`R1-1`,`R2-1`,`R1-2`,`R2-2`),
            funs(as.numeric(as.character(.))))

ggplot(sequence_data, aes(as.numeric(`R1-1`)))+
  geom_density(aes(fill = sequencer,
                   y = ..scaled..),
               alpha = 0.4)+
  labs(x = "Number of reads",
       y = "Density",
       fill = "Sequencer")+
  theme(legend.position = c(0.7, 0.8))
```

## Distribution of number of reads per library prep type
```{r}
ggplot(sequence_data, aes(as.numeric(`R1-1`)))+
  geom_density(aes(fill = libprep,
                   y = ..scaled..),
               alpha = 0.4)+
  labs(x = "Number of reads",
       y = "Density",
       fill = "Library prep kit")+
  theme(legend.position = c(0.7, 0.8))
```

## Distribution of number of reads per animal species
```{r}
ggplot(sequence_data, aes(as.numeric(`R1-1`)))+
  geom_density(aes(fill = species,
                   y = ..scaled..),
               alpha = 0.4)+
  labs(x = "Number of reads",
       y = "Density",
       fill = "Animal species")+
  theme(legend.position = c(0.7, 0.8))
```

```{r ARIBA analysis, include = FALSE}
megares_report_loc <- "../data/ariba/megares_results"
resfinder_report_loc <- "../data/ariba/resfinder_results"
ac_genes <- c("qnr","oqx")
mut_genes <- c("gyr","par","marR","soxR","acrR")

@@

# -------------------------------------- Functions

func_paste2 <- function(x) paste(unique(x[!is.na(x)]), collapse = ",")

@@

# Function that returns info on flag selection
check_flags <- function(df) {
  df <- df %>%
    select(ref, gene_names, flag, ref_ctg_change) %>%
    mutate(flag_result = flag %in% flag_selection,
           flag_result = as.integer(flag_result)) %>%
    rename("gene" = gene_names)
  return(df)
}

# Function that handles megares data and returns a data frame with information on whether a gene
# is mutated or not. Includes control for QRDR in gyrA.
create_mut_table <- function(df) {
  df <- df %>%
    mutate(ref_ctg_change = ifelse(ref_ctg_change == ".", "", ref_ctg_change),
           ref_nt = ifelse(ref_nt == ".", "", ref_nt),
           ctg_nt = ifelse(ctg_nt == ".", "", ctg_nt),
           ref_ctg_nt_change = paste(ref_nt, ctg_nt, sep = "-"),
           mutation = paste(ref_ctg_change, ref_ctg_nt_change, sep = "/"),
           mutation = ifelse(mutation == "/-", "0", mutation)) %>%
    select(ref, gene_names, flag, mutation) %>%
    filter(flag %in% flag_selection) %>%
    mutate(id = 1:n()) %>%
    spread(gene_names, mutation) %>%
    group_by(ref) %>%
    summarise_all(funs(func_paste)) %>%
    select(-c(id, flag)) %>%
    gather(gene, mut, -ref) %>%
    mutate(mut = ifelse(mut == "" | mut == "." | is.na(mut) == TRUE, 0, mut),
           result = ifelse(mut != 0, 1, 0),
           result = as.integer(result),
           type = "mut",
           nt_change = gsub("[^,]+?/([^,]+?)", "\\1", mut),
           mut = gsub("([^/]+)/[^,]+", "\\1", mut))
  return(df)
}

@@

# creates a data frame with one row per sample, and 1/0 results 
# for mutations in respective genes in columns
create_mut_report <- function(df) {
  df <- df %>%
    select(-mut) %>%
    group_by(id) %>%
    mutate(id2 = 1:n()) %>%
    spread(gene, result_total) %>%
    summarise_all(funs(func_paste)) %>%
    select(-c(id2, type))
  return(df)
}

# creates a data frame with one row per sample, and 1/0 results
# for acquired genes in columns
create_acquired_report <- function(df) {
  df <- df %>%
    group_by(id) %>%
    mutate(id2 = 1:n()) %>%
    spread(gene, result_total) %>%
    summarise_all(funs(func_paste)) %>%
    select(-c(id2, type))
  return(df)
}

@@

# Check flags
mut_flags <- check_flags(clean_mut_data) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref)

acquired_flags <- check_flags(clean_acquired_data) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref)

# Wrangle
mut_table <- create_mut_table(clean_mut_data)
mut_table_fixed <- fix_gyr_par_results(mut_table) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref)

mut_filtered <- filter_mut_table(mut_table_fixed)
acquired_table <- create_acquired_table(clean_acquired_data) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref)

acquired_filtered <- filter_acquired_table(acquired_table)

@@

mut_quant <- suppressWarnings(calc_no_of_mut(mut_table)) %>%
  left_join(id_data, by = "ref") %>%
  select(id, everything(), -ref)

@@

## Percent isolates with PMQR
```{r}
acquired_report %>%
  select(-id) %>%
  mutate_all(funs(as.numeric(.))) %>%
  mutate(total = rowSums(.),
         result = if_else(total != 0, 1, 0)) %>%
  group_by(result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 0, "Absent", "Present")) %>%
  spread(result, n) %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr))
```

## Percent isolates with specific qnr genes
```{r}
acquired_report %>%
  select(-id) %>%
  t() %>%
  as.data.frame(.) %>%
  mutate(Gene = rownames(.)) %>%
  mutate_at(vars(-Gene),
            funs(as.numeric(as.character(.)))) %>%
  mutate(Present = rowSums(.[,-286])) %>%
  select(c(Gene, Present)) %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total))
```

## Percent isolates with mutations in QRDR
```{r}
mut_report %>%
  select(-c(id, marR, nt_change)) %>%
  group_by_all() %>%
  count() %>%
  ungroup() %>%
  mutate_at(vars(c(gyrA, gyrB, parC, parE)),
            .funs = funs(as.numeric)) %>%
  mutate(type = ifelse(rowSums(.[,1:4]) == 0, 1, 0)) %>%
  select(n, type) %>%
  group_by(type) %>%
  summarise_all(funs(sum)) %>%
  mutate(type = ifelse(type == 0, "Present", "Absent")) %>%
  spread(type, n) %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total))
```

## Percent of isolates with specific mutation combinations in QRDR
```{r}
mut_quant %>%
  group_by(gyrA, gyrB, parC, parE) %>%
  count() %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(n/Total * 100,2),
         lwr = round(get_binCI(n, Total)[1], 2),
         upr = round(get_binCI(n, Total)[2], 2),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total))
```

## Percent isolates with specific nucleotide changes in QRDR
```{r}
suppressWarnings(clean_mut_data %>%
  mutate(ref_ctg_change = ifelse(ref_ctg_change == ".", "", ref_ctg_change),
         ref_nt = ifelse(ref_nt == ".", "", ref_nt),
         ctg_nt = ifelse(ctg_nt == ".", "", ctg_nt),
         ref_ctg_nt_change = paste(ref_nt, ctg_nt, sep = "-"),
         mutation = paste(ref_ctg_change, ref_ctg_nt_change, sep = "/"),
         mutation = ifelse(mutation == "/-", "0", mutation)) %>%
  select(ref, gene_names, flag, mutation) %>%
  filter(flag %in% flag_selection,
         gene_names %in% c("gyrA","gyrB","parC","parE")) %>%
  mutate(id = 1:n()) %>%
  spread(gene_names, mutation) %>%
  group_by(ref) %>%
  summarise_all(funs(func_paste2)) %>%
  select(-c(id, flag)) %>%
  gather(gene, mut, -ref) %>%
  mutate(mut = ifelse(mut == "" | mut == "." | is.na(mut) == TRUE, 0, mut),
         result = ifelse(mut != 0, 1, 0),
         result = as.integer(result),
         type = "mut") %>%
  separate(mut, into = paste("v", 1:12, sep = "_"), sep = ",") %>%
  gather(mut, value, paste("v", 1:12, sep = "_")) %>%
  separate(value, into = c("aa_change","nt_change"), sep = "/") %>%
  select(-mut) %>%
  rename("mut" = aa_change) %>%
  filter(is.na(nt_change) == FALSE) %>%
  fix_gyr_par_results(.) %>%
  filter(result_total == 1) %>%
  group_by(gene, mut, nt_change) %>%
  count() %>%
  separate(nt_change, into = c("Reference nt", "Contig nt"), sep = "-") %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(n/Total * 100,1),
         lwr = round(get_binCI(n, Total)[1],1),
         upr = round(get_binCI(n, Total)[2],1),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total)) %>%
  rename("Mutation" = mut))
```

## Total combinations
```{r}
test <- acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("marR","id")], by = "id") %>%
  left_join(mic_data[c("id","CIP","NAL")], by = "id") %>%
  select(-id) %>%
  group_by_at(vars(-c(CIP, NAL))) %>%
  summarise(CIP = ifelse(min(as.numeric(CIP)) == max(as.numeric(CIP)),
                         as.character(median(as.numeric(CIP))),
                         paste(min(as.numeric(CIP)), max(as.numeric(CIP)), sep = " - ")),
            NAL = ifelse(min(as.numeric(NAL)) == max(as.numeric(NAL)),
                         as.character(median(as.numeric(NAL))),
                         paste(min(as.numeric(NAL)), max(as.numeric(NAL)), sep = " - ")),
            n = n()) %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(n/Total * 100,1),
         lwr = round(get_binCI(n, Total)[1], 1),
         upr = round(get_binCI(n, Total)[2], 1),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total))
```

# Figures
## Percent isolates with PMQR and/or QRDR mutations in gyrA, gyrB, parC or parE
```{r}
total_report <- mut_report %>%
  left_join(acquired_report, by = "id") %>%
  gather(gene, value, -id) %>%
  mutate(present = ifelse(value == 1, gene, NA),
         ref = 1:n()) %>%
  spread(gene, value) %>%
  group_by(id) %>%
  summarise_all(funs(func_paste)) %>%
  select(-ref) %>%
  left_join(mic_data[c("id","CIP")], by = "id") %>%
  group_by(present,CIP) %>%
  count() %>%
  ungroup() %>%
  rowwise() %>%
  mutate(present = ifelse(present == "", "None", present),
         total = 285,
         percent = round(n/total * 100, 1),
         lwr = round(get_binCI(n, total)[1], 1),
         upr = round(get_binCI(n, total)[2], 1))

genes <- c(names(mut_report), names(acquired_report))
genes <- genes[!genes == "id"]

p1 <- ggplot(total_report, aes(reorder(present, as.numeric(-CIP)), percent, fill = factor(CIP)))+
  geom_col(color = "black")+
  labs(y = "Percent (%) isolates")+
  scale_fill_viridis(discrete = TRUE)+
  guides(fill = FALSE)+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.y = element_text(size = 10),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_blank(),
        legend.text = element_text(size = 8),
        legend.title = element_blank(),
        legend.position = "top",
        legend.spacing.x = unit(0.27, "cm"))

dot_report <- mut_report %>%
  left_join(acquired_report, by = "id") %>%
  gather(gene, value, -id) %>%
  mutate(present = ifelse(value == 1, gene, NA),
         ref = 1:n()) %>%
  spread(gene, value) %>%
  group_by(id) %>%
  summarise_all(funs(func_paste)) %>%
  left_join(mic_data[c("id","CIP")], by = "id") %>%
  select(-c(ref, id)) %>%
  ungroup() %>%
  mutate_at(vars(-present, CIP), .funs = as.numeric) %>%
  mutate(none = ifelse(rowSums(.[,genes]) == 0, 1, 0),
         present = ifelse(present == "", "None", present)) %>%
  gather(gene, value, -c(present,CIP)) %>%
  mutate(gene = ifelse(value == 0 & gene != "None", NA, gene),
         value = ifelse(gene == "None" & value == 0, NA, value)) %>%
  na.omit()

p2 <- ggplot(dot_report, aes(reorder(present, -CIP), gene, fill = gene))+
  geom_point(size = 2, pch = 21)+
  scale_fill_viridis(option = "B",
                     discrete = TRUE)+
  guides(fill = FALSE)+
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 8),
        axis.title = element_blank(),
        axis.ticks.x = element_blank())

plot_grid(p1, p2, nrow = 2, align = "v", rel_heights = c(3.5/5, 1.5/5))

## Percent QREC isolates with mutations in intrinsic genes
```{r}
gene_names <- names(mut_report)

gene_names <- gene_names[-c(1,2)]

mut_report %>%
    left_join(isolate_data, by = "id") %>%
    gather(key, value, gene_names) %>%
    group_by(key, value, species) %>%
    count() %>%
    ungroup() %>%
    mutate(value = if_else(value == 1, "Present", "Absent")) %>%
    spread(value, n, fill = 0) %>%
    rowwise() %>%
    mutate(
      Total = Present + Absent,
      Percent = round(Present / Total * 100, 1),
      lwr = round(get_binCI(Present, Total)[1], 1),
      upr = round(get_binCI(Present, Total)[2], 1)
    ) %>%
    ggplot(aes(key, Percent, fill = species)) +
    geom_col(color = "black",
             position = position_dodge(1)) +
    geom_errorbar(
      aes(ymin = lwr, ymax = upr),
      width = 0.6,
      position = position_dodge(1)
    ) +
    scale_fill_brewer(palette = "Paired") +
    labs(y = "Percent (%) of isolates") +
    guides(fill = FALSE) +
    theme_classic() +
    theme(
      axis.text.x = element_text(
        angle = 90,
        size = 12,
        hjust = 1,
        vjust = 0.4
      ),
      axis.title.x = element_blank(),
      axis.text.y = element_text(size = 12),
      axis.title.y = element_text(size = 14),
      strip.text = element_text(size = 12)
    ) +
    facet_wrap(~ species)
```
